---
title: "Developing Data Products-Week 2-Assignment"
author: "Roberto Lo Prejato"
date: "29 aprile 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## My first map

Using an R dataset i want to construct an interactive map with the package leafet

##Load Data
```{r load data}
library(leaflet)
data(breweries91)
head(breweries91)
class(breweries91)
```

I used the breweries dataset than contains the location (latitude and longitude) of `r dim(breweries91)[1]`  in Franconia; tt's a SpatialPointsDataFrame.

With next chunks I construct my map, using the clusterOptions I group the breweries depending on the zoom.

```{r myFirstMap}
myMap <- breweries91  %>% 
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup= paste(breweries91$brewery, breweries91$web, sep = " "), 
                   clusterOptions = markerClusterOptions())
myMap
```

When you select a single point in the popup you can look the name and the web site of the brewery.


