---
title: "Developing Data Products - Shiny App assignment"
author: "Roberto Lo Prejato"
date: "05 maggio 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Cluster Analysis with k-means Overview

This is an RStudio shiny application developed as a part of final project in the Developing Data Products course in Coursera Data Science Specialization track. 

The application show a cluster analysis with k-means and it's available at the link
[clusteranalysiskmeans](https://rloprejato.shinyapps.io/clusteranalysiskmeans/)

This analysis is an example of clustering customers from a wholesale customer database. 

You can download the data I’m using from the Berkley UCI Machine Learning Repository [here](https://archive.ics.uci.edu/ml/datasets/Wholesale+customers])
when you can find the data and attribute information.


## Focus on Data

```{r load data, include=FALSE}
fileurl <- "https://archive.ics.uci.edu/ml/machine-learning-databases/00292/Wholesale%20customers%20data.csv"
download.file(fileurl, destfile = "Wholesale customers data.csv")
dataset <- read.csv("Wholesale customers data.csv",header=T)
```
Some information about data

```{r cars, echo = TRUE}
dataset$Channel <- as.factor(dataset$Channel)
dataset$Region <- as.factor(dataset$Region)
summary(dataset)
```

In the analysis we will use only the numeric variables.

## Functionality

Ih this app you can find:

- A graph of total Within Sum of Squares for different number of cluster (k) to help to choose the correct one
- the Number of the rows considered for the analysis
- A heatmap to help to caracterize clusters

```{r prepare data, include=FALSE}
library(ggplot2);library(dplyr);library(tidyr)
top.n.custs <- function (data,cols,n=5) {
        idx.to.remove <-integer(0)
        for (c in cols){
                col.order <-order(data[,c],decreasing=T)
                idx <-head(col.order, n)
                idx.to.remove <-union(idx.to.remove,idx)
        return(idx.to.remove)
        }
}
top.custs <-top.n.custs(data = dataset,cols=3:8,n=5)
length(top.custs)
dataset[top.custs,]
data.rm.top<-dataset[-c(top.custs),]
#standardizzazione delle variabili
rescale_df <- data.rm.top %>%
        mutate(Fresh_scal = scale(Fresh),
               Milk_scal = scale(Milk),
               Grocery_scal = scale(Grocery),
               Frozen_scal = scale(Frozen),
               Detergents_Paper_scal = scale(Detergents_Paper),
               Delicassen_scal = scale(Delicassen)) %>%
        select(-c(1:8))
set.seed(76964057)
k <-kmeans(rescale_df, centers=5)
center <- k$centers
cluster <- c(1:5)
center_df <- data.frame(cluster, center)
center_reshape <- gather(center_df, features, values, Fresh_scal:Delicassen_scal)
```

```{r heatmap, echo=FALSE}
library(RColorBrewer)
# Create the palette
hm.palette <-colorRampPalette(rev(brewer.pal(10, 'RdYlGn')),space='Lab')
ggplot(data = center_reshape, aes(x = features, y = cluster, fill = values)) +
        scale_y_continuous(breaks = seq(1, 7, by = 1)) +
        geom_tile() +
        coord_equal() +
        scale_fill_gradientn(colours = hm.palette(90)) +
        theme_classic()
```

## Available Interacions

- Choose number of outliers to remove (default = 5)
- Choose interval value of k (default = from 2 to 20)
- Chooce is rescale variables (default = TRUE)
- Choose number of clusters for the heatmap (default = 5)



